### 2013-01-09 edupar-13/410.tex
410.tex: reorganized "Grading" and did initial work.

Pebbles kernels are graded in three ways: passing the ``hurdle'', running an automated test suite, and undergoing manual inspection by course staff.

\subsubsection{Hurdle}
%% TODO: Dave, write about the criteria (and what it means, i.e., "getting a shell up and running, getting processes to exit")
The hurdle is a set of criteria that Pebbles implementations must meet to be considered sastisfactory
(TODO: what are they?).
Towards the end of the kernel project, students fill out the ``hurdle form'', a checklist of these criteria.
Students who pass the hurdle turn in their kernels and move on to the shorter ``Pebbles Extension'' project.
Meanwhile, students who were unable to meet the
hurdle criteria on time receive additional time
to finish up and improve their code quality---this
requirement is based on our belief that important
learning experiences are obtained by solving the
hard problems,
which turn up at the end of the kernel implementation.
The hurdle criteria constitute 50\% of the kernel project's grade.

\subsubsection{Automated tests}
We run submitted kernels in an automated testing harness. The test suite is a number of userspace programs which test functionality ranging from the basic process lifecycle, to robustness against corner-case security vulnerabilities, to long-term stability under large stress tests.
Of course, due to the nondeterministic nature of many common bugs in student code, these tests can only provide a rough estimate of a submission's correctness, rather than verifying it with certainty.
Nevertheless, performance on these tests constitutes 30\% of the kernel project's grade.
(This hit-or-miss nature motivated our work on Landslide.)

>>>>

Pebbles kernels are graded through a combination
of three methods:
performance on a test suite,
compliance with ``hurdle criteria,''
and detailed code review by a member of the course staff.

\subsubsection{Automated tests}

While developing their code, students uncover both bugs
and design misunderstandings by running test code we
provide.
%Some tests are simple, exercising one feature or condition
%(e.g., allocating and freeing a large amount of memory),
%while other tests exercise a mix of kernel features
%simultaneously (creating and destroying processes,
%some of which do I/O while others handle or are killed
%by various exceptions) over an extended period of time.
The test suite is a number of user-space programs which test
functionality ranging from the basic process lifecycle, to robustness
against corner-case security vulnerabilities, to long-term stability
under large stress tests.
%
When students submit their kernels,
we use an automated testing harness to
run a superset of the public test suite.
%
Of course, due to the nondeterministic nature of many common bugs in student code, these tests can only provide a rough estimate of a submission's correctness, rather than verifying it with certainty.
Nevertheless, performance on these tests constitutes 30\% of the kernel project's grade.
(This hit-or-miss nature motivated our work on Landslide.)

\subsubsection{Hurdle}

%% TODO: Dave, write about the criteria (and what it means, i.e., "getting a shell up and running, getting processes to exit")
The hurdle is a set of criteria that Pebbles implementations must meet to be considered sastisfactory
(TODO: what are they?).
Towards the end of the kernel project, students fill out the ``hurdle form'', a checklist of these criteria.
Students who pass the hurdle turn in their kernels and move on to the shorter ``Pebbles Extension'' project.
Meanwhile, students who were unable to meet the
hurdle criteria on time receive additional time
to finish up and improve their code quality---this
requirement is based on our belief that important
learning experiences are obtained by solving the
hard problems,
which turn up at the end of the kernel implementation.
The hurdle criteria constitute 50\% of the kernel project's grade.
